Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-19 article.tex
Correction formulation critère du quadratn

\subsubsection{Quadrant criterion}
A version of this criterion was introduced here \cite{10201211} and used here \cite{art_del_paq}. Its goal is
to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
$k$-NN potential neigbours method.

It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
in each of the quadrants. The number of quadrants has been fixed to 6 (optimized here \cite{art_del_paq}).

The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between 0 and 
60 degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.

@@

The quadrant criterion is illustrated here Fig~\ref{fig:crit_qua}

>>>>

\subsubsection{Quadrant criterion}
As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
$k$-NN potential neigbours method.

It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
in each of the quadrants. The number of quadrants has been fixed to six \cite{art_del_paq}.

The criterion has been upgraded by adding the possibility to rotate the quadrants. The offset angle selected, which is between $0$ and 
$60$ degrees, is the one that maximises the sum of the distances of the potential neighbours to their closest quadrant delimitation.

@@

The quadrant criterion is illustrated in Fig~\ref{fig:crit_qua}.
